Missing Data: Current Practice in Football Research and Recommendations for Improvement

### 2020-11-07 paper/paper.Rmd
edit writing.

---
title: 'Missing Data: Current Practice in Football Research and Recommendations for Improvement'
bibliography: references.bib
output:
  bookdown::pdf_document2:
    toc: no
  html_document:
    keep_md: yes
    toc: yes
    toc_float: yes
  word_document:
    toc: yes
authors: David N Borg(1), Robert Nguyen(2), Nicholas J Tierney(3,4)
csl: sport-medicine.csl
---

@@

1.  Describe screening procedures **(define or example---think about screened out?)**.

@@

2.  State if missing data was explored. If there is missingness, provide a summary graphic (see figure XX)

@@

> Missing values of ZZ were imputed with a linear regression using terms XX. Missing values were imputed with the mean values

@@

Our survey of articles on football related topics showed that current practice of reporting missing data is poor, with only about one in 20 studies reporting missingness. We speculate that this result is representative of practice in the wider sports science literature. The extremely low reporting of missing data could suggest that this aspect of analysis receives little attention. To address this issue and assist researchers, we have provided recommendations for reporting and exploring missing data. Researchers should consider these recommendations, and pay greater attention to missing data and its influence on research results.

>>>>

---
title: 'Missing Data: Current Practice in Football Research and Recommendations for Improvement'
bibliography: references.bib
output:
  bookdown::pdf_document2:
    toc: no
  html_document:
    keep_md: yes
    toc: yes
    toc_float: yes
  word_document:
    toc: yes
authors: David N Borg(1,2), Robert Nguyen(3), Nicholas J Tierney(4,5)
csl: sport-medicine.csl
---

@@

1.  Describe screening procedures (define or example).

@@

2.  State if missing data was explored. If there is missingness, provide a summary graphic (see (Figure \@ref(fig:missing-overview)))

@@

> Missing values of ZZ were imputed with a linear regression using terms XX. Missing values were imputed with the mean values.

@@

Our survey of articles on football related topics showed that current practice of reporting missing data is poor, with only one in nine studies reporting missingness. We speculate that this result is representative of practice in the wider sports science literature. The extremely low reporting of missing data could suggest that this aspect of analysis receives little attention. To address this issue and assist researchers, we have provided recommendations for reporting and exploring missing data. Researchers should consider these recommendations, and pay greater attention to missing data and its influence on research results.
